Efficient Handling of String-Number Conversion

### 2019-11-21 evaluation.tex
Add table of checkLuhn results

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 20123 & 18490 &  3514 & 19149 \\ 
							& UNSAT    &  3858*   &  3841 &  3855 &  4521 & 3828 \\
							& $\times$ &  1977*   &  1457 &  3076 & 17386 & 2444 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &   128*   &    51 &    19 &    52 & 132 \\
							& UNSAT    &   287*   &   214 &   100 &   118 & 82 \\
							& $\times$ &   185*   &   335 &   481 &   430 & 386 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   871 &   881 &   651 & 778 \\
							& UNSAT    &  1784*   &  1785 &  1785 &  1787 & 1827 \\
							& $\times$ &    26*   &    10 &     0 &   228 & 61 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   610 &   316 &   605 & 688 \\
							& UNSAT    &   294*   &   255 &   206 &   217 & 339 \\
							& $\times$ &   269*   &   200 &   543 &   243 & 38 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 16* & 11 &   12 &    10 & 247 \\
							& UNSAT    &   814*   &   818 &   807 &   778 & 500 \\
							& $\times$ &     5*   &     6 &    16 &    47 & 88 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 9 &     6 &    16 & 311 \\
							& UNSAT    &  1030*   &  1025 &  1020 &   962 & 596 \\
							& $\times$ &     2*   &    11 &    19 &    67 & 138 \\ \hline
\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21675 & 19724 &  4848 & 21305  \\
							& UNSAT    &  8067*  &   7938 &  7773 &  8383 & 7172  \\
							& $\times$ &  2464*  &  2019 &   4135 & 18401 & 3155  \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraints + String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}                   			& {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1766 &  1025  &   333 \\ 
										 & UNSAT    &  16369*  & 15612 & 17234  & 15543 \\
										 & $\times$ &    202*  &  1549 &   668  &  3051 \\ \hline 
\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   586 &  1802  &   389 \\ 
										 & UNSAT    &    720*  &   666 &   744  &   729 \\
										 & $\times$ &   1014*  &  1394 &   100  &  1528 \\ \hline
\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20   &     5 &    16  &     4 \\ 
										 & UNSAT    &      0   &     0 &     0  &     0 \\
										 & $\times$ &      0   &    15 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}					 & SAT      &   3288*  &  2357 &  2843  &   726 \\ 
										 & UNSAT    &  17089*  & 16278 & 17978  & 16272 \\
										 & $\times$ &   1216*  &  2958 &   772  &  4595 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.097)
(3,0.078)
(4,0.098)
(5,0.098)
(6,0.161)
(7,0.236)
(8,0.307)
(9,0.26)
(10,0.211)
(11,0.228)
(12,0.33)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3-trau}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.4743)
(3,0.56052)
(4,0.36695)
(5,0.60905)
(6,22.06429)
(7,53.77536)
(8,118.41196)
(9,0.50559)
(10,120)
(11,0.42953)
(12,120)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3str3 (UNKNOWN if not timeout)}
\end{figure}

@@

We compare {\tool} with other state-of-the-art string solvers, namely CVC4(Relese-1.7)~\cite{cvc4Tool}, Z3(master:dde8da853)~\cite{z3}, \textsf{Z3-str3}(master:109dfc5e8)~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.

@@

All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS. The timeout was set to 10s for each test.
We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results. Occasionally, two of them report inconsistent (one SAT and one UNSAT) answers to the same test. To decide which solver reports the incorrect answer, we developed a validator, which takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtained a modified test, and re-evaluates the modified test by multiple solvers. If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results. Otherwise, we manually simplify and inspect the test until we get a conclusive result.

>>>>

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 20123 & 18490 &  3514 & 19149 \\ 
							& UNSAT    &  3858*   &  3841 &  3855 &  4521 & 3828 \\
							& $\times$ &  1977*   &  1457 &  3076 & 17386 & 2444 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &   128*   &    51 &    19 &    52 & 132 \\
							& UNSAT    &   287*   &   214 &   100 &   118 & 82 \\
							& $\times$ &   185*   &   335 &   481 &   430 & 386 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   871 &   881 &   651 & 778 \\
							& UNSAT    &  1784*   &  1785 &  1785 &  1787 & 1827 \\
							& $\times$ &    26*   &    10 &     0 &   228 & 61 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   610 &   316 &   605 & 688 \\
							& UNSAT    &   294*   &   255 &   206 &   217 & 339 \\
							& $\times$ &   269*   &   200 &   543 &   243 & 38 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 16* & 11 &   12 &    10 & 247 \\
							& UNSAT    &   814*   &   818 &   807 &   778 & 500 \\
							& $\times$ &     5*   &     6 &    16 &    47 & 88 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 9 &     6 &    16 & 311 \\
							& UNSAT    &  1030*   &  1025 &  1020 &   962 & 596 \\
							& $\times$ &     2*   &    11 &    19 &    67 & 138 \\ \hline
\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21675 & 19724 &  4848 & 21305  \\
							& UNSAT    &  8067*  &   7938 &  7773 &  8383 & 7172  \\
							& $\times$ &  2464*  &  2019 &   4135 & 18401 & 3155  \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraints + String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}                   			& {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1766 &  1025  &   333 \\ 
										 & UNSAT    &  16369*  & 15612 & 17234  & 15543 \\
										 & $\times$ &    202*  &  1549 &   668  &  3051 \\ \hline 
\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   586 &  1802  &   389 \\ 
										 & UNSAT    &    720*  &   666 &   744  &   729 \\
										 & $\times$ &   1014*  &  1394 &   100  &  1528 \\ \hline
\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20   &     5 &    16  &     4 \\ 
										 & UNSAT    &      0   &     0 &     0  &     0 \\
										 & $\times$ &      0   &    15 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}					 & SAT      &   3288*  &  2357 &  2843  &   726 \\ 
										 & UNSAT    &  17089*  & 16278 & 17978  & 16272 \\
										 & $\times$ &   1216*  &  2958 &   772  &  4595 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Comparison of {\tool}, CVC4, and Z3/Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.9}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 	  &  CVC4    	 &       Z3   & Z3-str3 \\ \hline
2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.27s)   & \textbf{SAT}(0.2s)  & $\times$ \\
3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(10.1s)  & \textbf{SAT}(0.1s)  & $\times$ \\
4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(48.7s) &   $\times$  & $\times$ \\
5 			& \textbf{SAT}(<0.1s)  &  $\times$     &   $\times$  & $\times$ \\
6 			& \textbf{SAT}(0.16s)  &  $\times$     & \textbf{SAT}(0.13s) & $\times$ \\
7 			& \textbf{SAT}(0.24s)  &  $\times$     &   $\times$  & $\times$ \\
8 			& \textbf{SAT}(0.31s)  &  $\times$     & \textbf{SAT}(0.37s) & $\times$ \\
9 			& \textbf{SAT}(0.26s)  &  $\times$     &   $\times$  & $\times$ \\
10 			& \textbf{SAT}(0.21s)  &  $\times$     & \textbf{SAT}(0.53s) & $\times$ \\
11 			& \textbf{SAT}(0.23s)  &  $\times$     & \textbf{SAT}(0.37s) & $\times$ \\
12 			& \textbf{SAT}(0.33s)  &  $\times$     & \textbf{SAT}(0.40s) & $\times$ \\ \hline
\end{tabular}}
\label{table:checkLuhn}
\end{table}

\hide{
\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.097)
(3,0.078)
(4,0.098)
(5,0.098)
(6,0.161)
(7,0.236)
(8,0.307)
(9,0.26)
(10,0.211)
(11,0.228)
(12,0.33)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3-trau}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.4743)
(3,0.56052)
(4,0.36695)
(5,0.60905)
(6,22.06429)
(7,53.77536)
(8,118.41196)
(9,0.50559)
(10,120)
(11,0.42953)
(12,120)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3str3 (UNKNOWN if not timeout)}
\end{figure}
}

@@

We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.

@@

All experiments were executed on a computer with 4-core CPU, 8 GiB RAM. The timeout was set to 10s for each test.
We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results. Occasionally, two of them report inconsistent (one SAT and one UNSAT) answers to the same test. To decide which solver reports the incorrect answer, we developed a validator, which takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtained a modified test, and re-evaluates the modified test by multiple solvers. If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results. Otherwise, we manually simplify and inspect the test until we get a conclusive result.
